Marlowe: implementing and analysing financial contracts on blockchain

### 2020-04-09 papers/marlowe2019/paper.tex
Update terminology

Cardano is a UTxO-based (unspent transaction output) blockchain, similar to Bitcoin~\cite{sok}.
It extends the Bitcoin model by allowing transaction outputs to hold a \emph{Data Script}.
As the name suggests, this is  a serialised data value used to store and communicate a contract state.
This allows us to create complex multi-transactional contracts.
In a nutshell, the EUTxO model looks like this:

@@

In order to spend an existing transaction output protected by a \emph{Validator},
one must create a transaction (a \emph{PendingTx}) that has an \emph{input} that references the transaction output,
and contains a \emph{Redeemer}, such that \texttt{Validator(Data Script, Redeemer, PendingTx)} evaluates to $True$.
A valid signature is required to spend a \emph{public key} transaction output.

@@

\noindent
Marlowe contract execution on the blockchain consists of a chain of transactions
where, at each stage, the remaining contract and its state are passed through the \emph{Data script},
and actions/inputs (i.e. \emph{choices} and \emph{money deposits}) are passed via the 
%SJT: is this right?
%AN: yes. [Input] is precisely the redeemer script. We could say that Value and SlotInterval are parts of PendingTx,
% but I think it's not that important here.
\emph{Redeemer}.
Each step in contract execution is a transaction that spends a Marlowe contract transaction output
by providing a valid input as \emph{Redeemer}, and produces a transaction output
with a the remaining Marlowe contract and the updated state.

We store the remaining contract in the \emph{Data script}, which makes it visible to everyone.
This simplifies contract reflection and retrospection.

@@

Contract creation is realised as a transaction
with at least one script output,
with the particular Marlowe contract in the data script, and protected by the Marlowe validator script.
Note that we do not place any restriction on the transaction inputs, which could use any other transaction
outputs, including other scripts. This gives this model optimal flexibility and composability.

@@

Marlowe contract execution consists of a chain of transactions,
where the remaining contract and state are passed through the \emph{data script},
and input actions (i.e. \texttt{choices}) are passed as \emph{redeemer scripts}.

>>>>

Cardano is a UTxO-based (unspent transaction output) blockchain, similar to Bitcoin~\cite{sok}.
It extends the Bitcoin model by allowing transaction outputs to hold a \emph{Dataum}.
As the name suggests, this is a serialised data value used to store and communicate a contract state.
This allows us to create complex multi-transactional contracts.
In a nutshell, the EUTxO model looks like this:

@@

In order to spend an existing transaction output protected by a \emph{Validator},
one must create a transaction (a \emph{Context}) that has an \emph{input} that references the transaction output,
and contains a \emph{Redeemer}, such that \texttt{Validator(Datum, Redeemer, Context)} evaluates to $True$.
A valid signature is required to spend a \emph{public key} transaction output.

@@

\noindent
Marlowe contract execution on the blockchain consists of a chain of transactions
where, at each stage, the remaining contract and its state are passed through the \emph{Datum},
and actions/inputs (i.e. \emph{choices} and \emph{money deposits}) are passed via the 
%SJT: is this right?
%AN: yes. [Input] is precisely the redeemer script. We could say that Value and SlotInterval are parts of Context,
% but I think it's not that important here.
\emph{Redeemer}.
Each step in contract execution is a transaction that spends a Marlowe contract transaction output
by providing a valid input as \emph{Redeemer}, and produces a transaction output
with a the remaining Marlowe contract and the updated state.

We store the remaining contract in the \emph{Datum}, which makes it visible to everyone.
This simplifies contract reflection and retrospection.

@@

Contract creation is realised as a transaction
with at least one script output,
with the particular Marlowe contract in the \emph{Datum}, and protected by the Marlowe validator script.
Note that we do not place any restriction on the transaction inputs, which could use any other transaction
outputs, including other scripts. This gives this model optimal flexibility and composability.

@@

Marlowe contract execution consists of a chain of transactions,
where the remaining contract and state are passed through the \emph{Datum},
and input actions (i.e. \texttt{choices}) are passed as \emph{redeemer scripts}.
